Devito for large scale elastic modelling and anisotropic inversion

### 2020-04-20 paper.tex
typos-george

% Default fixed font does not support bold face
\DeclareFixedFont{\ttb}{T1}{txtt}{bx}{n}{8.5} % for bold
\DeclareFixedFont{\ttm}{T1}{txtt}{m}{n}{8.5}  % for normal

@@

% Python style for highlighting
\newcommand\pythonstyle{\lstset{
    language=Python,
    basicstyle=\ttm,
    aboveskip=10pt,
    belowskip=10pt,
    otherkeywords={self},             % Add keywords here
    keywordstyle=\ttb\color{deepblue},
    emph={MyClass,__init__},          % Custom highlighting
    emphstyle=\ttb\color{deepred},    % Custom highlighting style
    stringstyle=\color{deepgreen},
    numbers=none,
    frame=tb,                         % Any extra options here
    showstringspaces=false            % 
}}

@@

\begin{python}
from devito import SparseTimeFunction
s = SparseTimeFunction(name="src",
                       grid=grid, npoint=1,
                       coordinates=x_s)
d = SparseTimeFunction(name="d", grid=grid,
                       npoint=1, nt=nt,
                       coordinates=x_r)
\end{python}

@@

\begin{python}
from devito import solve, Eq, Operator
eq = m * u.dt2 - u.laplace
update = Eq(u.forward, solve(eq, u.forward))
src_eqns = s.inject(u.forward, expr=s*dt**2/m)
d_eqns = d.interpolate(u)
\end{python}

@@

\begin{python}
dx_u = cos(theta) * cos(phi) * u.dx +
       cos(theta) * sin(phi) * u.dy -
       sin(theta) * u.dz
dxx_u = (cos(theta) * cos(phi) * dx_u).dx.T +
        (cos(theta) * sin(phi) * dx_u).dy.T -
        (sin(theta) * dx_u).dz.T
\end{python}

@@

\begin{table}
\centering
\begin{tabular}{ccc}
\toprule\addlinespace
spatial order & w/o optimizations & w/ optimizations\tabularnewline
\midrule
4 & 501 & 95\tabularnewline
8 & 539 & 102\tabularnewline
12 & 1613 & 160\tabularnewline
16 & 5489 & 276\tabularnewline
\bottomrule
\end{tabular}
\caption{Per-grid-point FLOPs of the finite-difference stencil for the
TTI wave-equation with different spatial discretization
orders.}\label{ttiFLOPs}
\end{table}

@@

\begin{python}
from devito import VectorTimeFunction,
                   TensorTimeFunction
v = VectorTimeFunction(name="v", grid=grid,
                       space_order=so,
                       time_order=1)
tau = TensorTimeFunction(name="t", grid=grid,
                         space_order=so,
                         time_order=1)
u_v = Eq(v.forward,
         damp * (v + s/rho*div(tau)))
u_t = Eq(tau.forward,
         damp * (tau + s * (l * diag(div(v.forward)) + mu * (grad(v.forward) + grad(v.forward).T))))
\end{python}

>>>>

% Default fixed font does not support bold face
\DeclareFixedFont{\ttb}{T1}{txtt}{bx}{n}{9} % for bold
\DeclareFixedFont{\ttm}{T1}{txtt}{m}{n}{9}  % for normal

@@

% Python style for highlighting
\newcommand\pythonstyle{\lstset{
    language=Python,
    basicstyle=\ttm,
    aboveskip=10pt,
    belowskip=10pt,
    otherkeywords={self},             % Add keywords here
    keywordstyle=\ttb\color{deepblue},
    emph={MyClass,__init__},          % Custom highlighting
    emphstyle=\ttb\color{deepred},    % Custom highlighting style
    stringstyle=\color{deepgreen},
    frame=tb,                         % Any extra options here
    showstringspaces=false            % 
}}

@@

\begin{python}
from devito import SparseTimeFunction
src = SparseTimeFunction(name="src", grid=grid,
                         npoint=1,
                         coordinates=x_s)
d = SparseTimeFunction(name="d", grid=grid,
                       npoint=1, nt=nt,
                       coordinates=x_r)
\end{python}

@@

\begin{python}
from devito import solve, Eq, Operator
eq = m * u.dt2 - u.laplace
update = Eq(u.forward, solve(eq, u.forward))
src_eqns = s1.inject(u.forward, expr=s1*dt**2/m)
d_eqns = d.interpolate(u)
\end{python}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{dx_u = cos(theta) * cos(phi) * u.dx + cos(theta) * sin(phi) * u.dy - sin(theta) * u.dz}
\NormalTok{dxx_u = (cos(theta) * cos(phi) * dx_u).dx.T + (cos(theta) * sin(phi) * dx_u).dy.T - (sin(theta) * dx_u).dz.T}
\end{Highlighting}
\end{Shaded}

@@

\begin{table}
\centering
\begin{tabular}{lll}
\toprule\addlinespace
spatial order & w/o optimizations & w/ optimizations\tabularnewline
\midrule
4 & 501 & 95\tabularnewline
8 & 539 & 102\tabularnewline
12 & 1613 & 160\tabularnewline
16 & 5489 & 276\tabularnewline
\bottomrule
\end{tabular}
\caption{Per-grid-point FLOPs of the finite-difference stencil for the
TTI wave-equation with different spatial discretization
orders.}\label{ttiFLOPs}
\end{table}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{v = VectorTimeFunction(name=}\StringTok{'v'}\NormalTok{, grid=model.grid, space_order=so, time_order=}\DecValTok{1}\NormalTok{)}
\NormalTok{tau = TensorTimeFunction(name=}\StringTok{'t'}\NormalTok{, grid=model.grid, space_order=so, time_order=}\DecValTok{1}\NormalTok{)}

\NormalTok{u_v = Eq(v.forward, model.damp * (v + s/rho*div(tau)))}
\NormalTok{u_t = Eq(tau.forward,  model.damp *  (tau + s * (l * diag(div(v.forward)) + mu * (grad(v.forward) + grad(v.forward).T))))}
\end{Highlighting}
\end{Shaded}
